Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-10 paper/paper.tex
feat(paper): Write about the not working tutorial cases

Most of the functionality that can be found in the official VM is also available in our NixOS VM and preCICE tutorials, such as the \textit{perpendicular-flap} can be run successfully.

>>>>

Most of the functionality that can be found in the official VM is also available in our NixOS VM and all preCICE tutorials could be run successfully, except \texttt{flow-over-heated-plate-steady-state} as the manual steps involved were unclear, \texttt{partitioned-heat-conduction-complex} and \texttt{partitioned-heat-conduction-direct} as the \texttt{mshr} python dependency was missing and \texttt{turek-hron-fsi3} as the tutorial needs \texttt{swak4foam}, an add-on to OpenFOAM, we were not able to package.
